---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multistatemodels

<!-- badges: start -->
<!-- badges: end -->

multistatemodels provides a package for simulating and fitting multistate models
especially semi-Markov models, to panel data and interval censored data. This is a
wrapper to the Julia package MultistateModels.jl. Add some more about why it is
good to call Julia from R...advantages, etc. 

## Installation

You can install the development version of multistatemodels from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ammateja/multistatemodels")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(multistatemodels)

#multistatemodels_setup()
multistatemodels <- multistatemodels_load()
df <- read.csv("H:/Projects/Jon/R package and Julia/Julia/derived_states_regen.csv")
d <- collapse_data(df[ ,-12], multistatemodels)

#h12 <- Hazard(formula = 0 ~ 1+mab, family = "sp", statefrom = 1, stateto=2,
#multistatemodels=multistatemodels, degree=1)
h12 <- Hazard(formula = 0 ~ 1+mab, family = "sp", statefrom = 1, stateto=2,
              multistatemodels=multistatemodels, degree=1, knots=5/7)
h23 <- Hazard(formula = 0 ~ 1+mab, family = "exp", statefrom = 2, stateto=3,
              multistatemodels=multistatemodels)
h24 <- Hazard(formula = 0 ~ 1+mab, family = "exp", statefrom = 2, stateto=4,
              multistatemodels=multistatemodels)
h45 <- Hazard(formula = 0 ~ 1+mab, family = "exp", statefrom = 4, stateto=5,
              multistatemodels=multistatemodels)
#h45 <- Hazard(formula = 0 ~ 1+mab, family = "exp", statefrom = 4, stateto=5,
#multistatemodels=multistatemodels, degree=1)

CensoringPatterns <- matrix(c(3, 1, 0, 1, 0, 0), nrow=1, ncol=6)

model <- multistatemodel(hazard = c(h12, h23, h24, h45), data = d[[1]], 
                         SamplingWeights = d[[2]], CensoringPatterns = CensoringPatterns,
                         nPatterns = 1, multistatemodels =multistatemodels)

```


